%
% Copyright © 2015 Peeter Joot.  All Rights Reserved.
% Licenced as described in the file LICENSE under the root directory of this GIT repository.
%
%----------------------------------------------------------------------------------------
%\part{Reading Notes}
   \mychapter{Fundamental parameters of Antennas.}
      \input{chapter2Notes.tex}
      \section{Problems.}
         \input{advancedantennaProblemSet1Problem1.tex}
         \input{advancedantennaProblemSet1Problem2.tex}
         \input{advancedantennaProblemSet1Problem3.tex}
         \input{advancedantennaProblemSet1Problem4.tex}
         \input{advancedantennaProblemSet1Problem5.tex}
         \input{advancedantennaProblemSet1Problem6.tex}
         \input{taiAndPereira.tex}
         \input{advancedantennaProblemSet2Problem1.tex}
         \input{advancedantennaProblemSet2Problem2.tex}
   \mychapter{Maxwell's equations.}
      \input{chapter3Notes.tex}
      \input{normalAndTangentialFields.tex}
      \input{energyMomentumWithMagneticSources.tex}
      \input{dualityTransformation.tex}
      \input{reciprocityTheorem.tex}
      \input{chapter3NotesNotation.tex}
      \section{Problems.}
          \input{advancedantennaProblemSet2Problem3.tex}
   \mychapter{Linear wire antennas.}
      \input{chapter4Notes.tex}
      \input{dualFarField.tex}
      \input{chapter4NotesPart2.tex}
      \input{resolvingFieldsIncidentOnPlane.tex}
      \input{imageTheorem.tex}
      \section{Problems.}
         \input{advancedantennaProblemSet2Problem4.tex}
         \input{advancedantennaProblemSet2Problem5.tex}
         \input{advancedantennaProblemSet3Problem1.tex}
         \input{advancedantennaProblemSet3Problem2.tex}
   \mychapter{Antenna arrays.}
      \input{tschebyscheff.tex}
      \input{chebychevDesign.tex}
      \input{chebychevSecondMethod.tex}
      \section{Problems.}
         %\input{advancedantennaProblemSet3Problem3.tex}
         \input{cornerCubeTakeII.tex}
         \input{tschebyscheffProblems.tex}
         \input{advancedantennaProblemSet4Problem1.tex}
         \input{advancedantennaProblemSet4Problem2.tex}
         \input{advancedantennaProblemSet4Problem3.tex}
         \input{advancedantennaProblemSet4Problem4.tex}
   \mychapter{Aperature antennas.}
      \section{Problems.}
         \input{advancedantennaProblemSet5Problem1.tex}
   \mychapter{Microstrip antennas.}
      \section{Problems.}
         \input{advancedantennaProblemSet5Problem2.tex}

%\part{Fields and Waves}
   \mychapter{Fields and Waves.}
   \input{cylindricalFieldSolution.tex}
   \input{impedanceTransformation.tex}
   \section{Problems.}
      \input{ExPlaneWave.tex}
